Analysis of Turkey's Trade with Selected Countries

### 2018-12-22 Draft/PresentationDraft.Rmd
.

---
title: "Analysis of Turkey's Trade with Selected Countries"
author: "Group Fou\\*R*"
date: Dec 26^th^, 2018
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
    template: quarterly-report.html

logo: channel4_logo.jpg
---

@@

@@

## Analysis of Trade Deficit by Countries and Years

@@

>>>>

---
title: "Analysis of Turkey's Trade with Selected Countries"
author: "Group Fou\\*R*"
date: "Dec 26^th^, 2018"
output:
  ioslides_presentation:
    smaller: yes
    template: quarterly-report.html
    widescreen: yes
logo: channel4_logo.jpg
---

@@

## Team Members & Abstract

* [Busra Koc](https://mef-bda503.github.io/pj18-busraakoc/) 
* [Emre Kemerci](https://mef-bda503.github.io/pj18-EmreKemerci/)
* [Muharrem Cakir](https://mef-bda503.github.io/pj18-muharremcakir81/)
* [Omer Bayir](https://mef-bda503.github.io/pj18-omerbayir/)
* [Salih Ucar](https://mef-bda503.github.io/pj18-ucarsal/)

In this term project, trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) is analysed. The aim of the project is to analyze Turkey's export and import characteristics by product groups considering the trade value and quantities.

@@

## Analysis | Trade Deficit by Countries and Years

@@

## Analysis | Countries Effect on Trade Deficit

```{r , fig.align="center"}
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  #filter (year == 2017)%>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

#Diverging Bars for normalized_Export_value
ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
  scale_fill_manual(name="Normalised Value", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="seagreen1", "below"="Red")) +  
  labs(subtitle="Normalised Net Value for 5 years by Country'", 
       title= "Diverging Bars") + 
  coord_flip()
```
<div class="centered" class="red2">
Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProAnly/)***
</div>

## Analysis | Correlation of Trade Deficit with FX Rate and BIST100 index

```{r, fig.align="center"}
fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)

colnames(usdR) <- c("DateR","ExchangeRate")
usd <- na.omit(usdR)
remove(usdR)

usdN<-usd %>% mutate(Date=dmy(DateR))
usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)

fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)

colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
  group_by(Year) %>% 
  summarise(Value = mean(Value)*1000)

sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
         Value_2017=Value_2017.y-Value_2017.x) %>%
  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)

joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
                                                                       variable == "Value_2014" ~ 2014,
                                                                       variable == "Value_2015" ~ 2015,
                                                                       variable == "Value_2016" ~ 2016,
                                                                       variable == "Value_2017" ~ 2017)) %>%
  select(Country,year,value)

deficitPerYear <- deficitPerCountry %>%
  group_by(year) %>% summarise(value=sum(value))

ggplot() + 
  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))

## Analysis | Analysis of the Import Unit Prices and Export Unit Prices

```{r, fig.align="center", fig.height=4.5, fig.width=10}

unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
  mutate(Unit_Price = Values/Quantity)
unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
  mutate(Unit_Price = Values/Quantity)

unit_price_import <- unit_price_import %>% mutate(type="Import") 
unit_price_export <- unit_price_export %>% mutate(type="Export")

joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable) %>% 
  filter(value  >0 & Ratio >0 & Ratio !=Inf ) #& Ratio <=1000 & value <=10000)

melted_data <- melted_data %>% mutate(Bins=0)
melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" &  Bins!="21-30") ) %>%  
  select(Country,Product_Label, year, Ratio, Bins) 
melted_data <- distinct(melted_data)

ggplot(melted_data, aes(Bins)) + 
  geom_bar(aes(fill=year), width = 0.5) +

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products whose ImportUnitPrice/ExportUnitPrice ratio more than 30",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```
<div class="centered" class="red2">
Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProUnitP/)***
</div>

## Analysis | K-Means Clustering

## Conclusion
